---
title: factors
output: github_document
bibliography: literature_files/references.bib
---

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

```{r, `load`, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.path = "README-")

folder <- "literature_files"; dir.create(folder)
download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", paste(folder, "references.bib", sep = "/"))

library(factors)
data(list = c("fama_french", "stambaugh"), package = "factors")
```

<style> body {text-align: justify} </style>

[factors](https://github.com/bautheac/factors/) packages various asset pricing research factor time series for convenient consumption by R users. The data is pulled directly from authors' website. Install from  with `devtools::install_github("bautheac/factors")`.

### Fama & French
The `fama_french` dataset provides the return (factors) and level (risk free rate) time series for the classic Fama/French asset pricing factors as used in their three [@fama_cross_section_1992; @fama_common_1993; @fama_size_1995] and most recently five-factor [@fama_five_factor_2015; @fama_dissecting_2016; @fama_international_2017] asset pricing models very popular to the asset pricing enthusiasts:
```{r, fama_french, echo = FALSE}
head(fama_french)
```

### Stambaugh et al
The `stambaugh` dataset provides the return (factors) and level (risk free rate) time series for various research asset pricing factors put together by Robert F. Stambaugh and collaborators including Lubos Pastor and Yu Yuan. The factors include traded & non-traded liquidity [@pastor_liquidity_2003], as well as market, size and two 'mispricing' factors: management & performance [@stambaugh_mispricing_2016]:  
```{r, stambaugh, echo = FALSE}
head(stambaugh)
```


### finRes   
Although the [factors](https://bautheac.github.io/factors/) package is self-contained it belongs to the [finRes](https://bautheac.github.io/finRes/) suite of packages where it helps with asset pricing research and analysis.  

## References

